Validation of an Actuator Line Model Coupled to a Dynamic Stall Model for Pitching Motions Characteristic to Vertical Axis Turbines

### 2016-06-13 paper.tex
Cite code repo

\documentclass[a4paper]{jpconf}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{cite}
\usepackage{gensymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb} 	%for symbols

@@

The ALM is a three-dimensional and unsteady aerodynamic model developed by
S{\o}rensen and Shen\cite{sorensen1999computation}, used to study the flow
around wind turbines. It is a combination of a solver of the Navier--Stokes equations
with a so-called actuator line technique, in which blades of the turbine are
represented by a distribution of body forces along lines. These forces
are determined using a dynamic stall model commonly based on empirical data.
This work uses the library turbinesFoam developed by Bachant et
al.~\cite{bachant2015simulating,Bachant2016-VAT-ALM}.

>>>>

\documentclass[a4paper]{jpconf}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{cite}
\usepackage{gensymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb} 	%for symbols
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,allcolors=blue]{hyperref}

@@

The ALM is a three-dimensional and unsteady aerodynamic model developed by
S{\o}rensen and Shen\cite{sorensen1999computation}, used to study the flow
around wind turbines. It is a combination of a solver of the Navier--Stokes equations
with a so-called actuator line technique, in which blades of the turbine are
represented by a distribution of body forces along lines. These forces
are determined using a dynamic stall model commonly based on empirical data.
This work uses the library turbinesFoam developed by Bachant et
al.~\cite{bachant2015simulating,Bachant2016-VAT-ALM,turbinesFoam-v0.0.7}.
